Refactoring the \texttt{nls()} function in R

### 2023-01-09 RefactoringNLS/RefactoringNLS.Rmd
updating paper

The convergence criterion above, the principal termination control of `nls()`, leaves out 
some possibilities that could
be useful for some problems. The package `nlsr` (@nlsr2019manual) already offers both 
the safeguarded relative offset test (**roffset**) as well as a **small sum of 
squares** test (**smallsstest**) that compares the latest evaluated sum of squared
(weighted) residuals to `e4` times the initial sum of squares, where
`e4 <- (100*.Machine$double.eps)^4` is approximately 2.43e-55.
(NOTE: For the purposes of this article, we use a developmental version of package
`nlsr` labelled `nlsr2`.)

@@

```{r SESingGrad}
reala <- -3; realb <- 5; realc <- 0.5; realr <- 0.7; realm <- 1 # underlying parameters
x <- 1:11 # x values; 11 data points
y <- reala + realb * realr^(x - realm) + realc * x # linear + exponential function
testdat <- data.frame(x, y) # save in a data frame
strt <- list(a = -3, b = 5, c = 0.5, r = 0.7, m = 1) # give programs a good start
jform <- y ~ a + b * r^(x - m) + c * x # Formula
library(nlsr2)
linexp2 <- try(nlxb(jform, data = testdat, start = strt, trace = FALSE))
linexp2 # Note singular values of Jacobian in rightmost column
# We get an error with nls()
linexp <- try(nls(jform, data = testdat, start = strt, trace = FALSE))
```

@@

As far as we can understand the logic in `nls()`, the Jacobian computation during
parameter estimation is carried out entirely within the called C-language program,
and the R code `function numericDeriv()`, part of `./src/library/stats/R/nls.R`
in the R distribution source code, is used to provide Jacobian information in 
the `nlsModel()` and `nlsModel.plinear()` functions.

The Jacobian used by `nlsr::nlxb()` is, by default, computed from analytic expressions, while that
of `nls()` mostly uses a numerical approximation. Some selfStart models do provide
"gradient" information. `minpack.lm::nlsLM()` invokes `numericDeriv()` in its local 
version of `nlsModel()`, but it appears to use an internal approximate Jacobian code from the 
original Fortran `minpack` code, namely, `lmdif.f`. Such differences in approach
can lead to different behaviour, though in our experience, one has to look for the
differences, as they are generally minor.

@@

<!-- nlsr2 has some extra info ?? -->

@@

```{r nlswtx, echo=TRUE}
weed <- c(5.308, 7.24, 9.638, 12.866, 17.069, 23.192, 31.443,
          38.558, 50.156, 62.948, 75.995, 91.972)
tt <- 1:12
weeddf <- data.frame(tt, weed)
wts <- 0.5^tt # simple weights
frmlogis <- weed ~ Asym/(1 + exp((xmid - tt)/scal))
Asym<-1; xmid<-1; scal<-1
nowt<-nls(weed ~ SSlogis(tt, Asym, xmid, scal)) # UNWEIGHTED
nowt
nowt$m$resid() # This has UNWEIGHTED residual and Jacobian. Does NOT take coefficients.
usewt <- nls(weed ~ SSlogis(tt, Asym, xmid, scal), weights=wts)
usewt
usewt$m$resid() # WEIGHTED. Does NOT take coefficients.
nmod0 <- nlsModel(frmlogis, data=weeddf, start=c(Asym=1, xmid=1, scal=1), wts=wts)
nmod0$resid() # Parameters are supplied in nlsModel() `start` above.
nmod <- nlsModel(frmlogis, data=weeddf, start=coef(usewt), wts=wts)
nmod$resid()
```

>>>>

The convergence criterion above, the principal termination control of `nls()`, leaves out 
some possibilities that could
be useful for some problems. The package `nlsr` (@nlsr2019manual) already offers both 
the safeguarded relative offset test (**roffset**) as well as a **small sum of 
squares** test (**smallsstest**) that compares the latest evaluated sum of squared
(weighted) residuals to `e4` times the initial sum of squares, where
`e4 <- (100*.Machine$double.eps)^4` is approximately 2.43e-55.

@@

```{r SESingGrad}
reala <- -3; realb <- 5; realc <- 0.5; realr <- 0.7; realm <- 1 # underlying parameters
x <- 1:11 # x values; 11 data points
y <- reala + realb * realr^(x - realm) + realc * x # linear + exponential function
testdat <- data.frame(x, y) # save in a data frame
strt <- list(a = -3, b = 5, c = 0.5, r = 0.7, m = 1) # give programs a good start
jform <- y ~ a + b * r^(x - m) + c * x # Formula
library(nlsr)
linexp2 <- try(nlxb(jform, data = testdat, start = strt, trace = FALSE))
linexp2 # Note singular values of Jacobian in rightmost column
# We get an error with nls()
linexp <- try(nls(jform, data = testdat, start = strt, trace = FALSE))
```

@@

As far as we can understand the logic in `nls()`, the Jacobian computation during
parameter estimation is carried out entirely within the called C-language program,
and the R code function `numericDeriv()`, part of `./src/library/stats/R/nls.R`
in the R distribution source code. This is used to provide Jacobian information in 
the `nlsModel()` and `nlsModel.plinear()` functions, which are not exported for 
general use.

The Jacobian used by `nlsr::nlxb()` is, by default, computed from analytic expressions, 
while that
of `nls()` mostly uses a numerical approximation. Some selfStart models do provide
"gradient" information. `minpack.lm::nlsLM()` invokes `numericDeriv()` in its local 
version of `nlsModel()`, but it appears to use an internal approximate Jacobian code from 
the original Fortran `minpack` code, namely, `lmdif.f`. Such differences in approach
can lead to different behaviour, though in our experience differences are usually minor.

@@

@@

```{r nlswtx, echo=TRUE}
weed <- c(5.308, 7.24, 9.638, 12.866, 17.069, 23.192, 31.443,
          38.558, 50.156, 62.948, 75.995, 91.972)
tt <- 1:12
weeddf <- data.frame(tt, weed)
wts <- 0.5^tt # simple weights
frmlogis <- weed ~ Asym/(1 + exp((xmid - tt)/scal))
Asym<-1; xmid<-1; scal<-1
nowt<-nls(weed ~ SSlogis(tt, Asym, xmid, scal)) # UNWEIGHTED
nowt
nowt$m$resid() # This has UNWEIGHTED residual and Jacobian. Does NOT take coefficients.
usewt <- nls(weed ~ SSlogis(tt, Asym, xmid, scal), weights=wts)
usewt
usewt$m$resid() # WEIGHTED. Does NOT take coefficients.
source("nlsModel.R")
nmod0 <- nlsModel(frmlogis, data=weeddf, start=c(Asym=1, xmid=1, scal=1), wts=wts)
nmod0$resid() # Parameters are supplied in nlsModel() `start` above.
nmod <- nlsModel(frmlogis, data=weeddf, start=coef(usewt), wts=wts)
nmod$resid()
```

### 2023-01-09 RefactoringNLS/RefactoringNLS.tex
updating paper

The convergence criterion above, the principal termination control of
\texttt{nls()}, leaves out some possibilities that could be useful for
some problems. The package \texttt{nlsr} (John C Nash and Duncan Murdoch
(\protect\hyperlink{ref-nlsr2019manual}{2019})) already offers both the
safeguarded relative offset test (\textbf{roffset}) as well as a
\textbf{small sum of squares} test (\textbf{smallsstest}) that compares
the latest evaluated sum of squared (weighted) residuals to \texttt{e4}
times the initial sum of squares, where
\texttt{e4\ \textless{}-\ (100*.Machine\$double.eps)\^{}4} is
approximately 2.43e-55. (NOTE: For the purposes of this article, we use
a developmental version of package \texttt{nlsr} labelled
\texttt{nlsr2}.)

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{reala }\OtherTok{\textless{}{-}} \SpecialCharTok{{-}}\DecValTok{3}\NormalTok{; realb }\OtherTok{\textless{}{-}} \DecValTok{5}\NormalTok{; realc }\OtherTok{\textless{}{-}} \FloatTok{0.5}\NormalTok{; realr }\OtherTok{\textless{}{-}} \FloatTok{0.7}\NormalTok{; realm }\OtherTok{\textless{}{-}} \DecValTok{1} \CommentTok{\# underlying parameters}
\NormalTok{x }\OtherTok{\textless{}{-}} \DecValTok{1}\SpecialCharTok{:}\DecValTok{11} \CommentTok{\# x values; 11 data points}
\NormalTok{y }\OtherTok{\textless{}{-}}\NormalTok{ reala }\SpecialCharTok{+}\NormalTok{ realb }\SpecialCharTok{*}\NormalTok{ realr}\SpecialCharTok{\^{}}\NormalTok{(x }\SpecialCharTok{{-}}\NormalTok{ realm) }\SpecialCharTok{+}\NormalTok{ realc }\SpecialCharTok{*}\NormalTok{ x }\CommentTok{\# linear + exponential function}
\NormalTok{testdat }\OtherTok{\textless{}{-}} \FunctionTok{data.frame}\NormalTok{(x, y) }\CommentTok{\# save in a data frame}
\NormalTok{strt }\OtherTok{\textless{}{-}} \FunctionTok{list}\NormalTok{(}\AttributeTok{a =} \SpecialCharTok{{-}}\DecValTok{3}\NormalTok{, }\AttributeTok{b =} \DecValTok{5}\NormalTok{, }\AttributeTok{c =} \FloatTok{0.5}\NormalTok{, }\AttributeTok{r =} \FloatTok{0.7}\NormalTok{, }\AttributeTok{m =} \DecValTok{1}\NormalTok{) }\CommentTok{\# give programs a good start}
\NormalTok{jform }\OtherTok{\textless{}{-}}\NormalTok{ y }\SpecialCharTok{\textasciitilde{}}\NormalTok{ a }\SpecialCharTok{+}\NormalTok{ b }\SpecialCharTok{*}\NormalTok{ r}\SpecialCharTok{\^{}}\NormalTok{(x }\SpecialCharTok{{-}}\NormalTok{ m) }\SpecialCharTok{+}\NormalTok{ c }\SpecialCharTok{*}\NormalTok{ x }\CommentTok{\# Formula}
\FunctionTok{library}\NormalTok{(nlsr2)}
\NormalTok{linexp2 }\OtherTok{\textless{}{-}} \FunctionTok{try}\NormalTok{(}\FunctionTok{nlxb}\NormalTok{(jform, }\AttributeTok{data =}\NormalTok{ testdat, }\AttributeTok{start =}\NormalTok{ strt, }\AttributeTok{trace =} \ConstantTok{FALSE}\NormalTok{))}
\NormalTok{linexp2 }\CommentTok{\# Note singular values of Jacobian in rightmost column}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## nlsr2  object: x 
## residual sumsquares =  0  on  11 observations
##     after  1    Jacobian and  1 function evaluations
##   name            coeff          SE       tstat      pval      gradient    JSingval   
## a                     -3            NA         NA         NA           0       26.49  
## b                      5            NA         NA         NA           0       9.615  
## c                    0.5            NA         NA         NA           0       2.466  
## r                    0.7            NA         NA         NA           0      0.1098  
## m                      1            NA         NA         NA           0   1.398e-16
\end{verbatim}

@@

As far as we can understand the logic in \texttt{nls()}, the Jacobian
computation during parameter estimation is carried out entirely within
the called C-language program, and the R code
\texttt{function\ numericDeriv()}, part of
\texttt{./src/library/stats/R/nls.R} in the R distribution source code,
is used to provide Jacobian information in the \texttt{nlsModel()} and
\texttt{nlsModel.plinear()} functions.

The Jacobian used by \texttt{nlsr::nlxb()} is, by default, computed from
analytic expressions, while that of \texttt{nls()} mostly uses a
numerical approximation. Some selfStart models do provide ``gradient''
information. \texttt{minpack.lm::nlsLM()} invokes
\texttt{numericDeriv()} in its local version of \texttt{nlsModel()}, but
it appears to use an internal approximate Jacobian code from the
original Fortran \texttt{minpack} code, namely, \texttt{lmdif.f}. Such
differences in approach can lead to different behaviour, though in our
experience, one has to look for the differences, as they are generally
minor.

@@

\begin{verbatim}
## Nonlinear regression model
##   model: weed ~ SSlogis(tt, Asym, xmid, scal)
##    data: parent.frame()
##   Asym   xmid   scal 
## 196.19  12.42   3.19 
##  residual sum-of-squares: 2.59
## 
## Number of iterations to convergence: 0 
## Achieved convergence tolerance: 1.13e-06
\end{verbatim}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{nmod0 }\OtherTok{\textless{}{-}} \FunctionTok{nlsModel}\NormalTok{(frmlogis, }\AttributeTok{data=}\NormalTok{weeddf, }\AttributeTok{start=}\FunctionTok{c}\NormalTok{(}\AttributeTok{Asym=}\DecValTok{1}\NormalTok{, }\AttributeTok{xmid=}\DecValTok{1}\NormalTok{, }\AttributeTok{scal=}\DecValTok{1}\NormalTok{), }\AttributeTok{wts=}\NormalTok{wts)}
\NormalTok{nmod0}\SpecialCharTok{$}\FunctionTok{resid}\NormalTok{() }\CommentTok{\# Parameters are supplied in nlsModel() \textasciigrave{}start\textasciigrave{} above.}
\end{Highlighting}
\end{Shaded}

@@

\begin{verbatim}
## > with(mm, table(Strip))
## Strip
## S01 S02 S03 
##   4   4   4 
## > nl <- nlevels(mm$Strip)
## > musc.1 <- nls(Length ~ cbind(1, exp(-Conc/th)), mm, start = list(th = 1), 
## +     algorithm = "plinear")
## > summary(musc.1)
## 
## Formula: Length ~ cbind(1, exp(-Conc/th))
## 
## Parameters:
##       Estimate Std. Error t value Pr(>|t|)    
## th       0.624      0.222    2.81   0.0203 *  
## .lin1   25.684      1.441   17.82  2.5e-08 ***
## .lin2  -26.631      6.147   -4.33   0.0019 ** 
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
## 
## Residual standard error: 2.96 on 9 degrees of freedom
## 
## Number of iterations to convergence: 5 
## Achieved convergence tolerance: 4.71e-07
## 
## > b <- coef(musc.1)
## > musc.2 <- nls(Length ~ a[Strip] + b[Strip] * exp(-Conc/th), data = mm, 
## +     start = list(a = rep(b[2], nl), b = rep(b[3], nl), th = b[1]))
## > summary(musc.2)
## 
## Formula: Length ~ a[Strip] + b[Strip] * exp(-Conc/th)
## 
## Parameters:
##    Estimate Std. Error t value Pr(>|t|)    
## a1  22.9277     0.5154   44.49  1.1e-07 ***
## a2  27.8606     0.5150   54.09  4.1e-08 ***
## a3  28.3426     1.0771   26.31  1.5e-06 ***
## b1 -44.1558    12.3900   -3.56    0.016 *  
## b2 -43.8084    12.3148   -3.56    0.016 *  
## b3 -32.8421     2.1553  -15.24  2.2e-05 ***
## th   0.5548     0.0808    6.86    0.001 ** 
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
## 
## Residual standard error: 0.798 on 5 degrees of freedom
## 
## Number of iterations to convergence: 6 
## Achieved convergence tolerance: 1.94e-06
\end{verbatim}

@@

\begin{verbatim}
## nlsr2  object: anlxb1 
## residual sumsquares =  9.4726  on  12 observations
##     after  12    Jacobian and  12 function evaluations
##   name            coeff          SE       tstat      pval      gradient    JSingval   
## b1                     2U           NA         NA         NA           0       23.35  
## b2               4.43325            NA         NA         NA   -2.16e-07           0  
## b3                     3U           NA         NA         NA           0           0
\end{verbatim}

>>>>

The convergence criterion above, the principal termination control of
\texttt{nls()}, leaves out some possibilities that could be useful for
some problems. The package \texttt{nlsr} (John C Nash and Duncan Murdoch
(\protect\hyperlink{ref-nlsr2019manual}{2019})) already offers both the
safeguarded relative offset test (\textbf{roffset}) as well as a
\textbf{small sum of squares} test (\textbf{smallsstest}) that compares
the latest evaluated sum of squared (weighted) residuals to \texttt{e4}
times the initial sum of squares, where
\texttt{e4\ \textless{}-\ (100*.Machine\$double.eps)\^{}4} is
approximately 2.43e-55.

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{reala }\OtherTok{\textless{}{-}} \SpecialCharTok{{-}}\DecValTok{3}\NormalTok{; realb }\OtherTok{\textless{}{-}} \DecValTok{5}\NormalTok{; realc }\OtherTok{\textless{}{-}} \FloatTok{0.5}\NormalTok{; realr }\OtherTok{\textless{}{-}} \FloatTok{0.7}\NormalTok{; realm }\OtherTok{\textless{}{-}} \DecValTok{1} \CommentTok{\# underlying parameters}
\NormalTok{x }\OtherTok{\textless{}{-}} \DecValTok{1}\SpecialCharTok{:}\DecValTok{11} \CommentTok{\# x values; 11 data points}
\NormalTok{y }\OtherTok{\textless{}{-}}\NormalTok{ reala }\SpecialCharTok{+}\NormalTok{ realb }\SpecialCharTok{*}\NormalTok{ realr}\SpecialCharTok{\^{}}\NormalTok{(x }\SpecialCharTok{{-}}\NormalTok{ realm) }\SpecialCharTok{+}\NormalTok{ realc }\SpecialCharTok{*}\NormalTok{ x }\CommentTok{\# linear + exponential function}
\NormalTok{testdat }\OtherTok{\textless{}{-}} \FunctionTok{data.frame}\NormalTok{(x, y) }\CommentTok{\# save in a data frame}
\NormalTok{strt }\OtherTok{\textless{}{-}} \FunctionTok{list}\NormalTok{(}\AttributeTok{a =} \SpecialCharTok{{-}}\DecValTok{3}\NormalTok{, }\AttributeTok{b =} \DecValTok{5}\NormalTok{, }\AttributeTok{c =} \FloatTok{0.5}\NormalTok{, }\AttributeTok{r =} \FloatTok{0.7}\NormalTok{, }\AttributeTok{m =} \DecValTok{1}\NormalTok{) }\CommentTok{\# give programs a good start}
\NormalTok{jform }\OtherTok{\textless{}{-}}\NormalTok{ y }\SpecialCharTok{\textasciitilde{}}\NormalTok{ a }\SpecialCharTok{+}\NormalTok{ b }\SpecialCharTok{*}\NormalTok{ r}\SpecialCharTok{\^{}}\NormalTok{(x }\SpecialCharTok{{-}}\NormalTok{ m) }\SpecialCharTok{+}\NormalTok{ c }\SpecialCharTok{*}\NormalTok{ x }\CommentTok{\# Formula}
\FunctionTok{library}\NormalTok{(nlsr)}
\NormalTok{linexp2 }\OtherTok{\textless{}{-}} \FunctionTok{try}\NormalTok{(}\FunctionTok{nlxb}\NormalTok{(jform, }\AttributeTok{data =}\NormalTok{ testdat, }\AttributeTok{start =}\NormalTok{ strt, }\AttributeTok{trace =} \ConstantTok{FALSE}\NormalTok{))}
\NormalTok{linexp2 }\CommentTok{\# Note singular values of Jacobian in rightmost column}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## residual sumsquares =  0  on  11 observations
##     after  1    Jacobian and  1 function evaluations
##   name            coeff          SE       tstat      pval      gradient    JSingval   
## a                     -3            NA         NA         NA           0       26.49  
## b                      5            NA         NA         NA           0       9.615  
## c                    0.5            NA         NA         NA           0       2.466  
## r                    0.7            NA         NA         NA           0      0.1098  
## m                      1            NA         NA         NA           0   9.798e-17
\end{verbatim}

@@

As far as we can understand the logic in \texttt{nls()}, the Jacobian
computation during parameter estimation is carried out entirely within
the called C-language program, and the R code function
\texttt{numericDeriv()}, part of \texttt{./src/library/stats/R/nls.R} in
the R distribution source code. This is used to provide Jacobian
information in the \texttt{nlsModel()} and \texttt{nlsModel.plinear()}
functions, which are not exported for general use.

The Jacobian used by \texttt{nlsr::nlxb()} is, by default, computed from
analytic expressions, while that of \texttt{nls()} mostly uses a
numerical approximation. Some selfStart models do provide ``gradient''
information. \texttt{minpack.lm::nlsLM()} invokes
\texttt{numericDeriv()} in its local version of \texttt{nlsModel()}, but
it appears to use an internal approximate Jacobian code from the
original Fortran \texttt{minpack} code, namely, \texttt{lmdif.f}. Such
differences in approach can lead to different behaviour, though in our
experience differences are usually minor.

@@

\begin{verbatim}
## Nonlinear regression model
##   model: weed ~ SSlogis(tt, Asym, xmid, scal)
##    data: parent.frame()
##   Asym   xmid   scal 
## 196.19  12.42   3.19 
##  residual sum-of-squares: 2.59
## 
## Number of iterations to convergence: 0 
## Achieved convergence tolerance: 1.12e-06
\end{verbatim}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{source}\NormalTok{(}\StringTok{"nlsModel.R"}\NormalTok{)}
\NormalTok{nmod0 }\OtherTok{\textless{}{-}} \FunctionTok{nlsModel}\NormalTok{(frmlogis, }\AttributeTok{data=}\NormalTok{weeddf, }\AttributeTok{start=}\FunctionTok{c}\NormalTok{(}\AttributeTok{Asym=}\DecValTok{1}\NormalTok{, }\AttributeTok{xmid=}\DecValTok{1}\NormalTok{, }\AttributeTok{scal=}\DecValTok{1}\NormalTok{), }\AttributeTok{wts=}\NormalTok{wts)}
\NormalTok{nmod0}\SpecialCharTok{$}\FunctionTok{resid}\NormalTok{() }\CommentTok{\# Parameters are supplied in nlsModel() \textasciigrave{}start\textasciigrave{} above.}
\end{Highlighting}
\end{Shaded}

@@

\begin{verbatim}
## > with(mm, table(Strip))
## Strip
## S01 S02 S03 
##   4   4   4 
## > nl <- nlevels(mm$Strip)
## > musc.1 <- nls(Length ~ cbind(1, exp(-Conc/th)), mm, start = list(th = 1), 
## +     algorithm = "plinear")
## > summary(musc.1)
## 
## Formula: Length ~ cbind(1, exp(-Conc/th))
## 
## Parameters:
##       Estimate Std. Error t value Pr(>|t|)    
## th       0.624      0.222    2.81   0.0203 *  
## .lin1   25.684      1.441   17.82  2.5e-08 ***
## .lin2  -26.631      6.147   -4.33   0.0019 ** 
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
## 
## Residual standard error: 2.96 on 9 degrees of freedom
## 
## Number of iterations to convergence: 5 
## Achieved convergence tolerance: 4.71e-07
## 
## > b <- coef(musc.1)
## > musc.2 <- nls(Length ~ a[Strip] + b[Strip] * exp(-Conc/th), data = mm, 
## +     start = list(a = rep(b[2], nl), b = rep(b[3], nl), th = b[1]))
## > summary(musc.2)
## 
## Formula: Length ~ a[Strip] + b[Strip] * exp(-Conc/th)
## 
## Parameters:
##    Estimate Std. Error t value Pr(>|t|)    
## a1  22.9277     0.5154   44.49  1.1e-07 ***
## a2  27.8606     0.5150   54.09  4.1e-08 ***
## a3  28.3426     1.0771   26.31  1.5e-06 ***
## b1 -44.1558    12.3900   -3.56    0.016 *  
## b2 -43.8084    12.3148   -3.56    0.016 *  
## b3 -32.8421     2.1553  -15.24  2.2e-05 ***
## th   0.5548     0.0808    6.86    0.001 ** 
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
## 
## Residual standard error: 0.798 on 5 degrees of freedom
## 
## Number of iterations to convergence: 6 
## Achieved convergence tolerance: 2.03e-06
\end{verbatim}

@@

\begin{verbatim}
## residual sumsquares =  9.4726  on  12 observations
##     after  12    Jacobian and  12 function evaluations
##   name            coeff          SE       tstat      pval      gradient    JSingval   
## b1                     2U           NA         NA         NA           0       23.35  
## b2               4.43325            NA         NA         NA   -2.16e-07           0  
## b3                     3U           NA         NA         NA           0           0
\end{verbatim}
